Considering scale in multilayer animal social networks

### 2020-06-13 paper/manuscript.Rmd
soc result

# Results

<!-- TODO: edge overlap can indicate if some associations are dependent on context -->

<!-- TODO: Add intro/general to results?-->
In general, individuals in multilayer networks became more connected as social
scale increased; however, this relationship varied by habitat type and season.
As social scale increased, mean graph strength for summer networks did not
change as the social threshold increased, but graph strength in winter networks
increased rapidly between 5 m and 50 m thresholds, followed by a plateau (Figure
\@ref(fig:socres)a). Layer relevance was stable around 0 during the summer but
increased for winter networks between 5 and 50 m social thresholds, then did not
change for any habitat types (Figure \@ref(fig:socres)b). This pattern suggests
the winter habitat layers captured most, if not all, of the potential
connections an individual would have across these networks. Layer similarity was
not very strong for any habitat type, indicating that summer and winter networks
are only weakly correlated. Furthermore, layer similarity in open habitats
showed more variation as social threshold increased compared to forage and
forest habitats (Figure \@ref(fig:socres)c). Connective redundancy was
relatively stable across social thresholds, especially after 50 m (Figure
\@ref(fig:socres)d). Taken together, these results suggest the optimal social
scale at which groups should be assigned is likely somewhere between ~20 - 100 m
based on the rate at which network metrics stabilized. For ungulates, groups are
often assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018;
Peignier et al. 2019), suggesting that given similar quantities of data, ~50 m
is likely an appropriate social scale for generating social networks in caribou
and similar species.

>>>>

# Results
<!-- TODO: edge overlap can indicate if some associations are dependent on context -->
<!-- TODO: Add intro/general to results?-->
<!-- major points then details -->

In general, individuals in multilayer networks became more connected as the
spatial distance threshold defining caribou social associations increased. Mean
graph strength differed across habitat layers with similar and higher graph
strength in open and forage layers, and lower strength in forest layers (Figure
\@ref(fig:socres)). Individual graph strength increased sharply between 5 m and
100 m across habitat classes followed by decrease in rate after 100 m. These
results suggest the optimal social scale at which groups should be assigned is
likely somewhere between ~20 - 100 m based on the rate at which network metrics
stabilized. For ungulates, groups are often assigned based on 50 m threshold
(Lingle 2003; Lesmeries et al. 2018; Peignier et al. 2019), suggesting that
given similar quantities of data, ~50 m is likely an appropriate social scale
for generating social networks in caribou and similar species.
